resistanceModelNotesAndy

### 2016-02-12 resistanceModelNotesAndy.Rmd
notes

** 11/2/16 **
~ added default curtis values to UI labels in server.r

@@

~ check on plotting of combined strategy, i think I may not be doing it right

>>>>

** 11/2/16 **
~ added default curtis values to UI labels in server.r
~ fixed plotting of combined strategy, i think I may not be doing it right

** 12/2/16 **
~ added position of Curtis inputs to the figures

@@
